\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-09-18 redaction/JEGeo/revision_JEGeo/revised_article/Online_Appendix/online_appendix_DHP_rev1.tex
changement texte (papier + annexe en ligne)

\begin{table}[htbp]
\centering
\footnotesize{
	\caption{Quality-of-fit diagnostic tests of the three models (Air, 3-digit level)}
	\label{tab:3models_diagnosis_air}%
	\input{TableA3_air.tex}
\begin{tablenotes}
	\tiny
	\item SER are weighted by value
	\item \textbf{Model (A): Iceberg transport costs only}
	\item \textbf{Model (B): With additive and ad-valorem transport costs}
	\item \textbf{Model (C): With additive transport costs only}
\end{tablenotes}
}
\end{table}%

\begin{table}[htbp]
	\centering
	\footnotesize{
		\caption{Quality-of-fit diagnostic tests of the three models (Ves, 3-digit level)}
		\label{tab:3models_diagnosis_vessel}%
		\input{TableA3_ves.tex}
		\begin{tablenotes}
			\tiny
			\item SER are weighted by value
			\item \textbf{Model (A): Iceberg transport costs only}
			\item \textbf{Model (B): With additive and ad-valorem transport costs}
			\item \textbf{Model (C): With additive transport costs only}
\end{tablenotes}
}
\end{table}%

@@

XXX UPDATE XXX In this section, we report the estimation results when we retain the 4-digit classification level ($s$=4-digit).

@@

\begin{table}[htbp]
  \centering
  \caption{Air: Transport costs estimates, selected years, 4-digit level}
\begin{center}
  \footnotesize{
    \begin{tabular}{l|cccccc}
   \hline\hline
Year & 1974  & 1981  & 1989  & 2001  & 2009  & 2013 \\ \hline
\multicolumn{7}{l}{\textbf{Model (a) - With only Ad-Valorem TC} ($\widehat{\tau}^{ice}-1$, in \%) }  \\
\hline
Mean  & 6.6 & 5.8 & 5.2 & 3.3 & 3.7 & 3.2 \\
Median & 5.2 & 4.4 & 4.1 & 2.1 & 2.7 & 2.6 \\
%Standard Error & 0.056 & 0.054 & 0.046 & \multicolumn{1}{c}{0.040} & \multicolumn{1}{c}{0.036} & \multicolumn{1}{c}{0.025}  \\
\hline
\multicolumn{7}{l}{\textbf{Model (b) - With Additive \& Ad-Valorem TC}}  \\ \hline
\multicolumn{7}{l}{\textit{Ad-valorem term }($\widehat{\tau}^{adv}-1$, in \%) }   \\ \hline
Mean  & 3.5 & 2.6 & 3.1 & 1.5 & 2.1 & 1.6  \\
Median & 2.5 & 1.7 & 1.9 & 1.0 & 1.7 & 1.4  \\
%Standard Error & 0.036 & 0.028 & 0.030 & \multicolumn{1}{c}{0.021} & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.015}  \\
\hline
\multicolumn{7}{l}{\textit{Additive term} ($\widehat{t}/\widetilde{p}$), in \%}    \\ \hline
Mean  & 2.6 & 2.1 & 1.7 & 1.2 &1.2 & 1.0 \\
Median & 1.2 & 0.6 & 0.6 & 0.5 & 0.4 & 0.4  \\
%Standard Error & 0.039 & 0.042 & 0.033 & \multicolumn{1}{c}{0.027} & \multicolumn{1}{c}{0.029} & \multicolumn{1}{c}{0.019} \\
\hline
\# observations & 14944 & 16844 & 25307 & \multicolumn{1}{c}{35005} & \multicolumn{1}{c}{38475} & \multicolumn{1}{c}{39460}  \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{11cm}{ \vspace{7pt}\scriptsize{Notes: TC = Transport Costs.
Statistics are obtained weighting each observation by its share in trade (mode-dependent).
Additive term expressed in fraction of fas price.}}}
\end{tabular}%
}
\end{center}
  \label{tab:result_air_rob}
\end{table}%

@@

\begin{table}[htbp]
  \centering
  \caption{Vessel: Measures of goodness of fit, 4-digit level}
\begin{center}
\label{tab:good_fit_ves_rob}%
  \footnotesize{
\begin{tabular}{l|cccccc}
\hline
\hline
      & \multicolumn{6}{c}{Year}                   \\
      & \multicolumn{1}{c}{1974} & \multicolumn{1}{c}{1981} & \multicolumn{1}{c}{1989} & \multicolumn{1}{c}{2001} & \multicolumn{1}{c}{2009} & \multicolumn{1}{c}{2013}  \\ \hline
\multicolumn{7}{l}{\textbf{R$^{2}$}} \\ \hline
Term I only & 0.50  & 0.45  & \multicolumn{1}{c}{0.47} & \multicolumn{1}{c}{0.41} & \multicolumn{1}{c}{0.37} & \multicolumn{1}{c}{0.35} \\
Terms A \& I & 0.66  & 0.62  & \multicolumn{1}{c}{0.62} & \multicolumn{1}{c}{0.58} & \multicolumn{1}{c}{0.51} & \multicolumn{1}{c}{0.46} \\ \hline
\multicolumn{7}{l}{\textbf{SER} }\\ \hline
Model (a) &    0.58   &   0.64    & \multicolumn{1}{c}{0.61} & \multicolumn{1}{c}{0.0.72} & \multicolumn{1}{c}{0.79} & \multicolumn{1}{c}{0.82} \\
Model (b) &   0.48    &    0.53   & \multicolumn{1}{c}{0.51} & \multicolumn{1}{c}{0.61} & \multicolumn{1}{c}{0.69} & \multicolumn{1}{c}{0.75} \\ \hline
\multicolumn{7}{l}{\textbf{Log-likelihood} } \\ \hline
Model (a)& -16460.1 & -16951.6 & \multicolumn{1}{c}{-26771.4} & \multicolumn{1}{c}{-39008.3} & \multicolumn{1}{c}{-43888.9} & \multicolumn{1}{c}{-47161.6} \\
Model (b) & -12743.65 & -13546.9 & \multicolumn{1}{c}{-21752.8} & \multicolumn{1}{c}{-33281.0} & \multicolumn{1}{c}{-39078.9} & \multicolumn{1}{c}{-43399.2}  \\ \hline
\multicolumn{7}{l}{\textbf{AIC criteria} } \\ \hline
Model (a) & 34464.2 & 35491.2 & \multicolumn{1}{c}{55272.9} & \multicolumn{1}{c}{79800.7} & \multicolumn{1}{c}{89459.8} & \multicolumn{1}{c}{95987.2}\\
Model (b) & 28271.3 & 29877.8 & \multicolumn{1}{c}{46595.6} & \multicolumn{1}{c}{69743.9} & \multicolumn{1}{c}{81155.7} & \multicolumn{1}{c}{89692.4} \\ \hline
\multicolumn{7}{l}{\textbf{Test LL}} \\ \hline
2$\times$(ll(UR) -ll(R)) & 12385.80 & 11226.8 & \multicolumn{1}{c}{17354.7} & \multicolumn{1}{c}{20113.5} & \multicolumn{1}{c}{16608.2} & \multicolumn{1}{c}{12589.6} \\
\# restrictions  & 797   & 814   & \multicolumn{1}{c}{881} & \multicolumn{1}{c}{910} & \multicolumn{1}{c}{886} & \multicolumn{1}{c}{874} \\
p-value & 0.000 & 0.000 & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{13cm}{ \vspace{7pt}\scriptsize{Notes: Model (a) = with only ad-valorem transport costs.
Model (b) = with additive \& ad-valorem
transport costs.
$R^{2}$ between the log of predicted ratio and the log of the observed ratio.
The number \# of restrictions is equal to the number of parameters estimated, i.e. the number of partner countries plus the number of products.}}}
\end{tabular}%
}
\end{center}
\end{table}%

@@

In this section, we complement Table 1 of the main text by reporting the year-to-year results of the estimation driven at the 3-digit classification level. Table \ref{tab_oa:result_ves_ally3} reports the results for each year over 1974-2019 for vessel; Table \ref{tab_oa:result_air_ally3} reports similar results for air transport. In both cases, we report the estimated values of the transport costs (weighted mean and median) when only ad-valorem costs are modeled (Model (A)), when both additive and ad-valorem costs are modeled (Model (B)) and when only additive costs are modeled (Model (A)).

@@

		\input{TableB1974_1987_ves.tex}
				\begin{tablenotes}
			\tiny
			\item Statistics are weighted by value
			\item \textbf{Model (A): With ad-valorem transport costs only}
			\item \textbf{Model (B): With additive and ad-valorem transport costs}
			\item \textbf{Model (C): With additive transport costs only}
		\end{tablenotes}

@@

	\caption{Continued}
	\begin{center}

		\input{TableB1988_2001_ves.tex}
				\begin{tablenotes}
			\tiny
			\item Statistics are weighted by value
			\item \textbf{Model (A): With ad-valorem transport costs only}
			\item \textbf{Model (B): With additive and ad-valorem transport costs}
			\item \textbf{Model (C): With additive transport costs only}
		\end{tablenotes}

@@

	\caption{Continued}
	\begin{center}

		\input{TableB2002_2015_ves.tex}
				\begin{tablenotes}
			\tiny
			\item Statistics are weighted by value
			\item \textbf{Model (A): Iceberg transport costs only}
			\item \textbf{Model (B): With additive and ad-valorem transport costs}
						\item \textbf{Model (C): With additive transport costs only}
		\end{tablenotes}

@@

	\caption{Continued}
	\begin{center}

		\input{TableB2016_2019_ves.tex}
				\begin{tablenotes}
			\tiny
			\item Statistics are weighted by value
			\item \textbf{Model (A): Iceberg transport costs only}
			\item \textbf{Model (B): With additive and ad-valorem transport costs}
			\item \textbf{Model (C): With additive transport costs only}
		\end{tablenotes}

@@

		\input{TableB1974_1987_air.tex}
				\begin{tablenotes}
			\tiny
			\item Statistics are weighted by value
			\item \textbf{Model (A): With ad-valorem transport costs only}
			\item \textbf{Model (B): With additive and ad-valorem transport costs}
			\item \textbf{Model (C): With additive transport costs only}
		\end{tablenotes}

@@

	\caption{Continued}
	\begin{center}

		\input{TableB1988_2001_air.tex}
				\begin{tablenotes}
			\tiny
			\item Statistics are weighted by value
			\item \textbf{Model (A): With ad-valorem transport costs only}
			\item \textbf{Model (B): With additive and ad-valorem transport costs}
			\item \textbf{Model (C): With additive transport costs only}
		\end{tablenotes}

@@

\caption{Continued}
\begin{center}

	\input{TableB2002_2015_air.tex}
			\begin{tablenotes}
		\tiny
		\item Statistics are weighted by value
		\\item \textbf{Model (A): With ad-valorem transport costs only}
		\item \textbf{Model (B): With additive and ad-valorem transport costs}
		\item \textbf{Model (C): With additive transport costs only}
	\end{tablenotes}

@@

\caption{Continued}
\begin{center}

	\input{TableB2016_2019_air.tex}
			\begin{tablenotes}
		\tiny
		\item Statistics are weighted by value
			\item \textbf{Model (A): With ad-valorem transport costs only}
			\item \textbf{Model (B): With additive and ad-valorem transport costs}
			\item \textbf{Model (C): With additive transport costs only}
	\end{tablenotes}

>>>>

\begin{table}[htbp]
\centering
\footnotesize{
	\caption{Quality-of-fit diagnostic tests, Air, 3-digit level}
	\label{tab:3models_diagnosis_air}%
	\input{TableA3_air.tex}
\begin{tablenotes}
	\tiny
	\item SER are weighted by value
	\item \textbf{Model (A): Iceberg transport costs only}
	\item \textbf{Model (B): With additive and ad-valorem transport costs}
	\item \textbf{Model (C): With additive transport costs only}
\end{tablenotes}
}
\end{table}%

\begin{table}[htbp]
	\centering
	\footnotesize{
		\caption{Quality-of-fit diagnostic tests, Vessel, 3-digit level}
		\label{tab:3models_diagnosis_vessel}%
		\input{TableA3_ves.tex}
		\begin{tablenotes}
			\tiny
			\item SER are weighted by value
			\item \textbf{Model (A): Iceberg transport costs only}
			\item \textbf{Model (B): With additive and ad-valorem transport costs}
			\item \textbf{Model (C): With additive transport costs only}
\end{tablenotes}
}
\end{table}%

@@

\textbf{XXX UPDATE XXX : Est-ce fait?} 
In this section, we report the estimation results when we retain the 4-digit classification level ($s$=4-digit).

@@

\begin{table}[htbp]
  \centering
  \caption{Air: Transport costs estimates, selected years, 4-digit level}
\begin{center}
  \footnotesize{
    \begin{tabular}{l|cccccc}
   \hline\hline
Year & 1974  & 1981  & 1989  & 2001  & 2009  & 2013 \\ \hline
\multicolumn{7}{l}{\textbf{Model (A) - With only Ad-Valorem TC} ($\widehat{\tau}^{ice}-1$, in \%) }  \\
\hline
Mean  & 6.6 & 5.8 & 5.2 & 3.3 & 3.7 & 3.2 \\
Median & 5.2 & 4.4 & 4.1 & 2.1 & 2.7 & 2.6 \\
%Standard Error & 0.056 & 0.054 & 0.046 & \multicolumn{1}{c}{0.040} & \multicolumn{1}{c}{0.036} & \multicolumn{1}{c}{0.025}  \\
\hline
\multicolumn{7}{l}{\textbf{Model (B) - With Additive \& Ad-Valorem TC}}  \\ \hline
\multicolumn{7}{l}{\textit{Ad-valorem term }($\widehat{\tau}^{adv}-1$, in \%) }   \\ \hline
Mean  & 3.5 & 2.6 & 3.1 & 1.5 & 2.1 & 1.6  \\
Median & 2.5 & 1.7 & 1.9 & 1.0 & 1.7 & 1.4  \\
%Standard Error & 0.036 & 0.028 & 0.030 & \multicolumn{1}{c}{0.021} & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.015}  \\
\hline
\multicolumn{7}{l}{\textit{Additive term} ($\widehat{t}/\widetilde{p}$), in \%}    \\ \hline
Mean  & 2.6 & 2.1 & 1.7 & 1.2 &1.2 & 1.0 \\
Median & 1.2 & 0.6 & 0.6 & 0.5 & 0.4 & 0.4  \\
%Standard Error & 0.039 & 0.042 & 0.033 & \multicolumn{1}{c}{0.027} & \multicolumn{1}{c}{0.029} & \multicolumn{1}{c}{0.019} \\
\hline
\# observations & 14944 & 16844 & 25307 & \multicolumn{1}{c}{35005} & \multicolumn{1}{c}{38475} & \multicolumn{1}{c}{39460}  \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{11cm}{ \vspace{7pt}\scriptsize{Notes: TC = Transport Costs.
Statistics are obtained weighting each observation by its share in trade (mode-dependent).
Additive term expressed in fraction of fas price.}}}
\end{tabular}%
}
\end{center}
  \label{tab:result_air_rob}
\end{table}%

@@

\begin{table}[htbp]
  \centering
  \caption{Vessel: Measures of goodness of fit, 4-digit level}
\begin{center}
\label{tab:good_fit_ves_rob}%
  \footnotesize{
\begin{tabular}{l|cccccc}
\hline
\hline
      & \multicolumn{6}{c}{Year}                   \\
      & \multicolumn{1}{c}{1974} & \multicolumn{1}{c}{1981} & \multicolumn{1}{c}{1989} & \multicolumn{1}{c}{2001} & \multicolumn{1}{c}{2009} & \multicolumn{1}{c}{2013}  \\ \hline
\multicolumn{7}{l}{\textbf{R$^{2}$}} \\ \hline
Term I only & 0.50  & 0.45  & \multicolumn{1}{c}{0.47} & \multicolumn{1}{c}{0.41} & \multicolumn{1}{c}{0.37} & \multicolumn{1}{c}{0.35} \\
Terms A \& I & 0.66  & 0.62  & \multicolumn{1}{c}{0.62} & \multicolumn{1}{c}{0.58} & \multicolumn{1}{c}{0.51} & \multicolumn{1}{c}{0.46} \\ \hline
\multicolumn{7}{l}{\textbf{SER} }\\ \hline
Model (a) &    0.58   &   0.64    & \multicolumn{1}{c}{0.61} & \multicolumn{1}{c}{0.0.72} & \multicolumn{1}{c}{0.79} & \multicolumn{1}{c}{0.82} \\
Model (b) &   0.48    &    0.53   & \multicolumn{1}{c}{0.51} & \multicolumn{1}{c}{0.61} & \multicolumn{1}{c}{0.69} & \multicolumn{1}{c}{0.75} \\ \hline
\multicolumn{7}{l}{\textbf{Log-likelihood} } \\ \hline
Model (a)& -16460.1 & -16951.6 & \multicolumn{1}{c}{-26771.4} & \multicolumn{1}{c}{-39008.3} & \multicolumn{1}{c}{-43888.9} & \multicolumn{1}{c}{-47161.6} \\
Model (b) & -12743.65 & -13546.9 & \multicolumn{1}{c}{-21752.8} & \multicolumn{1}{c}{-33281.0} & \multicolumn{1}{c}{-39078.9} & \multicolumn{1}{c}{-43399.2}  \\ \hline
\multicolumn{7}{l}{\textbf{AIC criteria} } \\ \hline
Model (a) & 34464.2 & 35491.2 & \multicolumn{1}{c}{55272.9} & \multicolumn{1}{c}{79800.7} & \multicolumn{1}{c}{89459.8} & \multicolumn{1}{c}{95987.2}\\
Model (b) & 28271.3 & 29877.8 & \multicolumn{1}{c}{46595.6} & \multicolumn{1}{c}{69743.9} & \multicolumn{1}{c}{81155.7} & \multicolumn{1}{c}{89692.4} \\ \hline
\multicolumn{7}{l}{\textbf{Test LL}} \\ \hline
2$\times$(ll(UR) -ll(R)) & 12385.80 & 11226.8 & \multicolumn{1}{c}{17354.7} & \multicolumn{1}{c}{20113.5} & \multicolumn{1}{c}{16608.2} & \multicolumn{1}{c}{12589.6} \\
\# restrictions  & 797   & 814   & \multicolumn{1}{c}{881} & \multicolumn{1}{c}{910} & \multicolumn{1}{c}{886} & \multicolumn{1}{c}{874} \\
p-value & 0.000 & 0.000 & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{13cm}{ \vspace{7pt}\scriptsize{Notes: Model (A) = with only ad-valorem transport costs.
Model (B) = with additive \& ad-valorem
transport costs.
$R^{2}$ between the log of predicted ratio and the log of the observed ratio.
The number \# of restrictions is equal to the number of parameters estimated, i.e. the number of partner countries plus the number of products.}}}
\end{tabular}%
}
\end{center}
\end{table}%

@@

In this section, we complement Table 1 of the main text by reporting the year-to-year results of the estimation driven at the 3-digit classification level. Table \ref{tab_oa:result_ves_ally3} reports the results for each year over 1974-2019 for vessel; Table \ref{tab_oa:result_air_ally3} reports similar results for air transport. In both cases, we report the estimated values of the transport costs (weighted mean and median) when only ad-valorem costs are modeled (Model (A)), when both additive and ad-valorem costs are modeled (Model (B)) and when only additive costs are modeled (Model (A)). In all tables, statistics are weighted by value.

@@

		\input{TableB1974_1987_ves.tex}
				%\begin{tablenotes}
%			\tiny
%			\item
%			\item \textbf{Model (A): With ad-valorem transport costs only}
%			\item \textbf{Model (B): With additive and ad-valorem transport costs}
%			\item \textbf{Model (C): With additive transport costs only}
%		\end{tablenotes}

@@

	\caption{Vessel, Yearly estimates, Continued}
	\begin{center}

		\input{TableB1988_2001_ves.tex}
				%\begin{tablenotes}
%			\tiny
%			\item Statistics are weighted by value
%			\item \textbf{Model (A): With ad-valorem transport costs only}
%			\item \textbf{Model (B): With additive and ad-valorem transport costs}
%			\item \textbf{Model (C): With additive transport costs only}
%		\end{tablenotes}

@@

	\caption{Vessel, Yearly estimates, Continued}
	\begin{center}

		\input{TableB2002_2015_ves.tex}
				%\begin{tablenotes}
%			\tiny
%			\item Statistics are weighted by value
%			\item \textbf{Model (A): Iceberg transport costs only}
%			\item \textbf{Model (B): With additive and ad-valorem transport costs}
%			\item \textbf{Model (C): With additive transport costs only}
%		\end{tablenotes}

@@

	\caption{Vessel, Yearly estimates, Continued}
	\begin{center}

		\input{TableB2016_2019_ves.tex}
			%	\begin{tablenotes}
%			\tiny
%			\item Statistics are weighted by value
%			\item \textbf{Model (A): Iceberg transport costs only}
%			\item \textbf{Model (B): With additive and ad-valorem transport costs}
%			\item \textbf{Model (C): With additive transport costs only}
%		\end{tablenotes}

@@

		\input{TableB1974_1987_air.tex}
				%\begin{tablenotes}
%			\tiny
%			\item Statistics are weighted by value
%			\item \textbf{Model (A): With ad-valorem transport costs only}
%			\item \textbf{Model (B): With additive and ad-valorem transport costs}
%			\item \textbf{Model (C): With additive transport costs only}
%		\end{tablenotes}
%		
	\end{center}
	\label{tab_oa:result_air_ally3}%
\end{table}%

@@

	\caption{Air, Vessel, Yearly estimates, Continued}
	\begin{center}

		\input{TableB1988_2001_air.tex}
				%\begin{tablenotes}
%			\tiny
%			\item Statistics are weighted by value
%			\item \textbf{Model (A): With ad-valorem transport costs only}
%			\item \textbf{Model (B): With additive and ad-valorem transport costs}
%			\item \textbf{Model (C): With additive transport costs only}
%		\end{tablenotes}
%		
	\end{center}
	\label{tab_oa:result_air_ally3}%
\end{table}%

@@

\caption{Air, yearly estimates, Continued}
\begin{center}

	\input{TableB2002_2015_air.tex}
			%\begin{tablenotes}
%		\tiny
%		\item Statistics are weighted by value
%		\\item \textbf{Model (A): With ad-valorem transport costs only}
%		\item \textbf{Model (B): With additive and ad-valorem transport costs}
%		\item \textbf{Model (C): With additive transport costs only}
%	\end{tablenotes}

@@

\caption{Air, yearly estimates, Continued}
\begin{center}

	\input{TableB2016_2019_air.tex}
			%\begin{tablenotes}
%		\tiny
%		\item Statistics are weighted by value
%			\item \textbf{Model (A): With ad-valorem transport costs only}
%			\item \textbf{Model (B): With additive and ad-valorem transport costs}
%			\item \textbf{Model (C): With additive transport costs only}
%	\end{tablenotes}
